\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Large \scshape Natalie Piontek} \\ \vspace{1pt}
    \textbf{Senior Software Engineer} \\ \vspace{1pt}
    \small 314-482-4876 $|$ \href{mailto:nataliep769@gmail.com}{\underline{nataliep769@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/natalie-piontek-91988592/}{\underline{linkedin.com/in/natalie-piontek-91988592/}} $|$
    {\small Boulder, CO}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
      \resumeItemListStart
        \resumeItem{Full-stack engineer with 7+ years of professional experience and specializations in Python and Java. Emphasis on healthcare technology with 4 years of experience in HIPAA-compliant ecosystems and 2 years of experience in EMR/EHR development. Excellent communicator with advanced degrees in English and journalism.}
      \resumeItemListEnd
%

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Backend Engineer}{December 2022 -- November 2024}
      {HealthJoy}{Remote}
      \resumeItemListStart
        \resumeItem{Data Pipeline Transformation - Implemented a queueing system and parallelized processing for an ETL pipeline that ingested sensitive medical data via S3, increasing the data completion rate from 50\%  to 80\%  over 9 months.}
        \resumeItem{Observability - Achieved service maturity by establishing comprehensive monitoring with Grafana alerts, PromQL, and Redash dashboards. Wrote an SOP for third party administrator stakeholders, expediting the remediation of file ingestion errors.}
        \resumeItem{Personalized Healthcare Recommendations - Developed and shipped a healthcare recommendation engine, serving 7M+ personalized recommendations across 34 healthcare categories to 1.5M+ members. Integrated historical health goal survey responses into member profiles, creating 448,000 new recommendations (444 percent increase).}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer II}{September 2020 -- November 2022}
      {Daugherty}{Remote}
      \resumeItemListStart
        \resumeItem{Financial Account Migration - Developed a portability feature for financial advisors, facilitating data transfer between account types and reducing the number of manual processes.}\resumeItem{Technical Leadership - Designed and taught the curriculum for an internal software engineering bootcamp that covered end-to-end testing, OOP, automated testing frameworks (Selenium), and software development best practices. Trained 15+ junior engineers.}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{January 2019 -- August 2020}
      {RevolutionEHR}{Remote}
      \resumeItemListStart
        \resumeItem{Tech Stack Modernization - Rewrote a legacy ophthalmology EHR administrative portal from Java 5, Flex, and MXML to Java 8, Angular, and HTML.}
    \resumeItemListEnd
    \resumeSubheading
      {Intern Backend Developer}{October 2017 -- January 2019}
      {Maritz LLC.}{St. Louis, MO}
      \resumeItemListStart
        \resumeItem{Employee Motivation - Developed RESTful, unit- and integration-tested Java APIs for employee motivation software.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
         \textbf{Programming Languages and Frameworks}{: Python (FastAPI, Flask, SQLAlchemy, GINO), Java (Spring), JavaScript, TypeScript, React, Angular, SQL} \\
         \textbf{Cloud Infrastructure and DevOps}{: AWS, Docker, Kubernetes, CI/CD Implementation, Terraform, Git, Jenkins, BitBucket, GitLab, GitHub} \\
         \textbf{Monitoring and System Reliability}{: Prometheus, Grafana, Mimir, Splunk, PromQL, Dynatrace, Sentry} \\
         \textbf{Database}{: PostgreSQL, RabbitMQ, High-Volume Data Processing} \\
        \textbf{Architecture and System Integration}{: Microservices Architecture, RESTful API Design, Event-Driven Architecture, Solution Architecture,  ETL Pipelines} \\
        \textbf{Leadership and Methodologies}{: Technical Leadership,  Agile, Scrum, Cross-functional Collaboration}
    }}
 \end{itemize}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indiana University}{Bloomington, IN}
      {Bachelor of Arts in English Literature}{August 2009 -- May 2014}
    \resumeSubheading
      {Syracuse University}{Syracuse, NY}
      {Master of Arts in Arts Journalism}{June 2014 -- June 2015}
    \resumeSubheading
      {LaunchCode}{St. Louis, MO}
      {Certificate in Computer Science}{January 2017 -- June 2017}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}